% Memorandum
\newpage
\section*{Memorandum}
\addcontentsline{toc}{section}{Memorandum}
{\large
    \textbf{MEMO} \par
    \textbf{TO: Chief Operating Officer} \par
    \textbf{FROM: Team\#2414787} \par
    \textbf{DATE: February 6} \par
    \textbf{SUBJECT: Momentum in Tennis} \par
}

\par
\partLine

In accordance with your requests, We have established several customized models to answer your questions. We have been working on these models for the past four days and we are now ready to present the results. We will also provide you with some suggestions on how to guide the players to make timely adjustments on the field.

\subsection*{Results: }
We used an AHP-TOPSIS model to analyze player momentum in the tournament. Check out the Figure \ref{fig:M3} of the 2023 Wimbledon Gentlemen's final below.\par

Some coaches seemed to underestimate the impact of momentum on the game. The model we have developed is able to predict matches using momentum with about 65\% accuracy. Although this is not a very high rate of correctness, it shows that momentum can influence the game.\par

For the swing problem in the match, we built a decision tree model to obtain the key indicators that cause the swing (turn) of the game and find that the serving side, the winner of the previous set, and the score of sets are the key indicators. In addition, we built an LSTM model to predict the possible swing and the advantage of the LSTM is that it is able to utilize the data of the previous matches, and the prediction accuracy of our optimal model reached 0.81, which is believed to be sufficient for most situations. \par

Our model also has some limitations; the weather, player injuries, venues, and other factors have a very significant impact on the game; we will improve the model in the future to take these factors back into account. At the same time, due to the lack of data, the machine learning model has not been well trained; I believe that in the future, under the improvement, the accuracy of the model will be significantly improved (plus the limitations of the fourth question). \par

\subsection*{Findings and Recommandations}
Based on the statistics we've got, Athletes need to focus on the influences of the serve, the game situation, the winner of the previous game, etc., during the match. We recommend focusing on these main factors and designing tactics with his characteristics. Maximize the duration of his side's advantage and minimize fluctuations in the game that are not in his favor. 
